SST_patterns

### 2019-11-01 SST_patterns.Rmd
fixed

Loading the data
```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
```

@@

@@

@@

>>>>

Loading the data
```{r}
load("Data/OISST_upwell_base.RData")
load("Data/CMC_upwell_base.RData")
load("Data/SACTN_upwell_base.RData")
load("Data/MUR_upwell_base.RData")
```

@@

MUR_upwell_base <- km_func(df = MUR_upwell_base)
MUR_upwell_base$distance_km <- as.numeric(MUR_upwell_base$distance_km)

@@

############
#####MUR

MUR_filtered <- year_func(df = MUR_upwell_base)

MUR_SEAPOINT <- MUR_filtered %>% 
  filter(site == "Sea Point")
MUR_SB <- MUR_filtered %>% 
  filter(site == "Saldanha Bay")
MUR_PN <- MUR_filtered %>% 
  filter(site == "Port Nolloth")
MUR_LB <- MUR_filtered %>% 
  filter(site == "Lamberts Bay")
```

@@

##########
### MUR
(MUR_SP_pl <- plot_loli_func(df = MUR_SEAPOINT))
(MUR_SB_pl <- plot_loli_func(df = MUR_SB))
(MUR_PN_pl <- plot_loli_func(df = MUR_PN))
(MUR_LB_pl <- plot_loli_func(df = MUR_LB))

MUR_SP_pl <- MUR_SP_pl +
  ggtitle("D.") #Sea Point
MUR_SB_pl <- MUR_SB_pl +
  ggtitle("C.") # Saldanha Bay
MUR_PN_pl <- MUR_PN_pl +
  ggtitle("B.")        # Port Nolloth
MUR_LB_pl <- MUR_LB_pl +
  ggtitle("A.")#Lamberts Bay

combined_MUR_pl_2 <- ggarrange(MUR_SB_pl, MUR_SP_pl)

combined_MUR_pl_1 <- ggarrange(MUR_LB_pl, MUR_PN_pl)

########
